### 2017-10-13 Gruba/04-uc.tex

\begin{table}[!htb]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_u$, $\#E_u$, $R_{ee}$, $\#B_u$, $R_{oc}$, $\#W_r$				\\	\midrule
categorical data			& $U_t$				\\	\midrule
normalized vectors			& $P_t$, $P_g$, $P_f$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

Hence, the said distance regarding the complex vectors ($Y\ =\ (Y_0, Y_1, ...)$ and $Z\ =\ (Z_0, Z_1, ...)$ ) in K-Gru, named \gd{}, could be deduced as:
%
\begin{equation}
\label{eq:gd}
D_g(Y, Z) = \sum_{\substack{e}} G_e
\end{equation}
where the distance on each dimension $G_e$ is given by:
%
\begin{equation}
\label{eq:ge}
G_e =
  \begin{cases}
    (Y_e - Z_e)^2       & \quad \text{if } Y_e/Z_e \text{ is numerical}\\
    H_e\ (1\ or\ 0)       	& \quad \text{if } Y_e/Z_e \text{ is categorical}\\
    Y_e \cdot Z_e  		& \quad \text{if } Y_e/Z_e \text{ is of normalized vector}
  \end{cases}
\end{equation}

>>>>

\begin{table}[!htb]
\centering
\begin{small}
%\caption{Types of Dimensional Data in \textit{Feature Data} Vector}
\caption{Dimension Types in \textit{Feature Data} Vector}
\vspace{0.3cm}
\label{tbl:data-type}
\begin{tabular}{ll}
\toprule
\multicolumn{1}{c}{\textbf{type}} & \multicolumn{1}{c}{\textbf{data dimensions}}	\\	\midrule \midrule
numerical data				& $\#R_u$, $\#E_u$, $R_{ee,u}$, $\#B_u$,\\
                            &  $R_{oc,u}$, $\#W_{r,u}$,$\#W_{t,u}$				\\	\midrule
categorical data			& $G_u$,$P_u$,$U_{t,u}$				\\	\midrule
normalized vectors			& $P_{rt,u}$, $P_{rg,u}$,$P_{tt,u}$,$P_{tg,u}$,$P_{f,u}$			\\ \bottomrule
\end{tabular}
\end{small}
\end{table}

@@

Hence, the said distance regarding the complex vectors ($Y\ =\ (Y_0, Y_1, ...)$ and $Z\ =\ (Z_0, Z_1, ...)$ ) in K-Gru, named \gd{}, could be deduced as:
%
\begin{equation}
\label{eq:gd}
D_g(Y, Z) = \sum_{\substack{e}} G_e
\end{equation}
where the distance on each dimension $G_e$ is given by:
%
\begin{equation}
\label{eq:ge}
G_e =
  \begin{cases}
    (Y_e - Z_e)^2       & \quad \text{if } Y_e/Z_e \text{ is numerical}\\
    H_e\ (1\ or\ 0)       	& \quad \text{if } Y_e/Z_e \text{ is categorical}\\
    1 - Y_e \cdot Z_e  		& \quad \text{if } Y_e/Z_e \text{ is of normalized vector}
  \end{cases}
\end{equation}
